The Shot Predictor

### 2022-10-17 Papers/PaperForReview.tex
basketball + pose detection paper

Before a posture recognition algorithm can be made, though, there needs to be an understanding of what postures we are trying to recognize [1]. One example solution is shown below. 
%
\begin{quotation}
  Level 1: Divide posture into two categories based on whether or not the motion is cyclic \\
  \indent - Instantaneous Movement 
  \indent - Continuous Movement 
  \newline
  \indent Level 2: Divide posture into seven postures \\
  \indent - Walking 
  \indent - Running 
  \indent - Dribbling 
  \indent - Jumping 
  \indent - Shooting 
  \indent - Passing 
  \indent - Catching 
\end{quotation}
%

Notice how these actions are exclusive to basketball. The algorithm is only concerned with basketball, and will deem all other actions as unnecessary as such. 
A popular tool used for key feature detection in order to track certain postures is SIFT [1]. The upper and lower limbs are pivotal in determining what an athlete is doing, 
so using SIFT to identify and track limbs would be useful for understanding an athlete's posture.

>>>>

%-------------------------------------------------------------------------
\subsection{Basketball and Pose Estimation}

Collecting and analyzing basketball player's posture data is important and 
highly sought after in the scientific basketball community in order to help
coaches improve their training plan, and help players maximize their training 
outputs. As it stands, the current technology faces some combination of 
high inefficiency or high error rates. Rather than using wearable, inertial sensor
recognition equipment, which tends to be expensive and not applicable to how a 
real game is played, it was decided to use posture recognition via video instead.
In order to improve the athlete's training effect, a gesture recognition method 
based on feature extraction and machine learning was implemented in order to 
acquire the upper limb and lower limb features needed to classify a posture.  
The action posture data of players was collected through image feature extraction
methods, and with the method of feature selection, accurate classification and recognition
of basketball shooting gestures can be made. This paper is similar to our project because 
it attempts to take and encode data about motion of a player through pose estimation to 
make predictions, but our project solely focuses on the motion of a shot, and predicting 
the outcome of the shot.

%
